Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-12 paper/main.tex
updated comment to pearson

  However, this conclusion is not necessarily accurate. Globular clusters lose mass and evaporate over time, leading to an incomplete catalog of perturbers. Moreover, the present-day masses used in our simulations are likely lower than the historical masses of these clusters. For example, \citet{2024ApJ...976...54P}. conducted a study simulating the dissolution of a realistic globular cluster population, demonstrating that the historical population was significantly larger, with masses totaling XXX. This implies that more perturbers could have been present in the past, potentially increasing the frequency and number of gaps in Palomar~5's stream.

>>>>

  However, this conclusion is not necessarily accurate. Globular clusters lose mass and evaporate over time, leading to an incomplete catalog of perturbers. Moreover, the present-day masses used in our simulations are likely lower than the historical masses of these clusters. For example, \citet{2024ApJ...976...54P} conducted a study simulating the dissolution of a realistic globular cluster population, in the aims of identifying how many stellar streams we should expect in the Milky Way and used a mock catalog of globular clusters with an initial amount with masses above 10~$^4 M_\odot$ totaling at about 10,000 clusters. This implies that more perturbers could have been present in the past, potentially increasing the frequency and number of gaps in Palomar~5's stream.
